Turbulence in compact to giant H~II regions

### 2023-04-24 strucfunc_paper.tex
Finish revision of NGC 346

Figure~\ref{fig:strucfunc-fit-MC}b shows the structure function of NGC 346.
The value of the observed \(\sigma\pos^2 = \SI{30}{km^{2}.s^{-2}}\) is obtained at \(r_0 = \SI{2.3}{pc} \) (in this case there is a good agreement with the derived values from our model which are \(\sigma\pos^2 = \SI{33}{km^{2}.s^{-2}}\) and \(r_0 = \SI{2.4}{pc} \)).
The observed value of \(2\sigma\pos^2\) corresponds to \(r = \SI{10}{pc} \), though, at this scale the \(B(r)\) value is just below the \(2\sigma\pos^2\), but the structure function seems to plateau at those values.
Above this scales the structure function shows a periodic pattern with a spatial wavelength of \SI{\sim 10}{pc} and a dispersion of \(\SI{6}{km^{2}.s^{-2}}\).
Unlike the Carina nebula, this oscillating pattern is below the \(2\sigma\pos^2\) value.
The seeing value is \SI{0.11}{pc} (\(s_0\)=\SI{0.9}{\arcsecond}) and just one point of the structure functions lies below this value.
Considering the first point above this \(s_0\) value to be valid, which corresponds to \SI{2.5}{km^{2}.s^{-2}} at \(r = \SI{0.2}{pc} \) the slope for \(\sigma\pos^2\) and \(2\sigma\pos^2\) we obtain \num{1.01} and \num{0.81}, respectively, while our derived value is \num{0.95}.

>>>>

Figure~\ref{fig:strucfunc-fit-MC}b shows the structure function of NGC 346.
\startNEW
The model-derived parameters are \(\sigma\pos^2 = \SI{33 \pm 3}{km^{2}.s^{-2}}\),
\(r_0 = \SI{2.4\pm 0.3}{pc} \)), and \(m = 0.95 \pm 0.07\).
These agree very well with the empirically derived parameters.
At large scales, an oscillatory behavior in \(B(r)\) is observed for \(r > \SI{10}{pc}\),
consistent with a periodic pattern with wavelength \(\lambda \approx \SI{15}{pc}\) and amplitude \(\SI{6}{km^{2}.s^{-2}}\).
Inspection of the velocity field (Figure~\ref{fig:velocity-maps}) shows that this pattern is predominantly oriented along the north-south direction and corresponds to the spacing between the filaments of molecular gas.
\stopNEW
